working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
changes

For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species. Closely related species are more likely to have similar traits @letten2015. The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion (REF) and therefore studies predict and show a greater negative effect of closely related species (REFS). Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species Thomson et al. (1982) Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013). The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen where closely related species cand lead to greater detrimental effects @arceo2016.

>>>>

For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species. Closely related species are more likely to have similar traits @letten2015. The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion @arceo2011 and therefore studies predict and show a greater negative effect of closely related species @ashman2013; @arceo2016. Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999. Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013). The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen where closely related species cand lead to greater detrimental effects @arceo2016.

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
changes

For the understanding at what level or intensity the interference of
pollen can occur is important to consider the relatedness of the
interacting species. Closely related species are more likely to have
similar traits Letten and Cornwell (2015). The similarity in traits
between closely related species can lead to higher chances of ovule
usurpation/abortion (REF) and therefore studies predict and show a
greater negative effect of closely related species (REFS). Few studies
however, have focused on the impacts of heterospecific pollen on fitness
of distantly related species Thomson et al. (1982) Galen and Gregory
(1989) Neiland and Wilcock (1999). Yet, most insects and most stigmas
have been found to carry multiple species of foreign pollen with little
attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang
and Huang (2013). The relative amounts of closely/far related pollen
that arrives to a stigma gives a first snapshoot where pollen
competition can occur and improves the understanding of how important
the reduction of fitness can be from heterospecific pollen where closely
related species cand lead to greater detrimental effects Arceo-Gómez and
Ashman (2016).

@@

>>>>

For the understanding at what level or intensity the interference of
pollen can occur is important to consider the relatedness of the
interacting species. Closely related species are more likely to have
similar traits Letten and Cornwell (2015). The similarity in traits
between closely related species can lead to higher chances of ovule
usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
predict and show a greater negative effect of closely related species
Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
studies however, have focused on the impacts of heterospecific pollen on
fitness of distantly related species Galen and Gregory (1989); Neiland
and Wilcock (1999). Yet, most insects and most stigmas have been found
to carry multiple species of foreign pollen with little attention to
degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang
(2013). The relative amounts of closely/far related pollen that arrives
to a stigma gives a first snapshoot where pollen competition can occur
and improves the understanding of how important the reduction of fitness
can be from heterospecific pollen where closely related species cand
lead to greater detrimental effects Arceo-Gómez and Ashman (2016).

@@

\hypertarget{ref-arceo2011}{}
Arceo-Gómez, G., and T.-L. Ashman. 2011. Heterospecific pollen
deposition: Does diversity alter the consequences? New Phytologist
192:738--746.
